Allowing Stable Groups of Prosumers to Enter the Market through Proper Aggregation

### 2014-09-11 Article.tex
update

\section{Introduction}
\label{sec:introduction}
% no \IEEEPARstart
One of the key ideas in the smart grid revolves around the introduction of communication means inside the power grids. That could enable complex improvements in the energy management and lead progressively to a greener energetic system \cite{Ramchurn} \cite{WuHamedHuangBook2011}. Distributed energy resources (DER) such as wind turbines or photovoltaic panels are not supposed to emerge in only in solar farms, but also in residential areas. Together with electric vehicles, and demand side management tools, they will constitute the building blocks which will help to turn the today pure energy consumers into true actors of the grid operation \cite{Ramchurn}. Such agents that both consume and produce energy are ready to make concessions (appliances delays, V2G…) to ensure grid stability are called prosumers \cite{Rathnayaka2012} \cite{Ramchurn}.

There seems to have a clear consensus on the benefit of having a bidirectional communication flows between prosumers and the grid as most of the demand side management concepts have proposed \cite{WuHamedHuangBook2011}. Nevertheless as the number of active prosumers is expected to rise, it is safe to assume there is a need for more complex communication pattern (such as coalitions) that will help to decrease the communication burden and in the mean time satisfy the multiple requirements of the power grid management. The formation of coalition inside the smart grid environment could be applied to various agents such as the self sufficient micro-grids\cite{Pahwa}, the virtual power plants (VPP), sizable and adjustable plants \cite{Braun} \cite{Ramchurn}, or fleet of electric vehicles that back up the grid in some emergency situations (V2G) \cite{Ramchurn}, are just a few use case where the coalition of multiple agents can enhance grid reliability and in the mean time reduce the communication burden.

In this paper, we focus on how to statistically improve the production stability by carefully forming coalitions of prosumers that have greater probability of staying in acceptable range of production. By using prediction techniques, we form coalitions that meet the contract values ranges proposed by the grid, enabling it to schedule its production accordingly. Meeting contract values for the prosumer are especially relevant in power trade conditions, where energy is traded based on day-ahead predictions. In this context, participants should try to minimize its prediction error in order to maintain a stable state for the grid. They may even occur some penalty if the production deviate from its initial contract value. However, it is pertinent for both side to maintain the production as stable as possible, for the prosumer the stability (with renewable energy source) will impact its net gain and for the power grid it helps to maintain its reliability.

>>>>

\section{Introduction}
\label{sec:introduction}
% no \IEEEPARstart
One of the key ideas in the smart grid revolves around the introduction of communication means inside the power grids. This could enable complex improvements in the energy management and lead progressively to a greener energetic system \cite{Ramchurn} \cite{WuHamedHuangBook2011}. Distributed energy resources (DER) such as wind turbines or photovoltaic panels are not supposed to emerge only in remote farms, but also in residential areas. Together with electric vehicles, and demand side management tools, they will constitute the building blocks which will help to turn the today pure energy consumers into true actors of the grid operation \cite{Ramchurn}. Such agents that both consume and produce energy are ready to make concessions (appliances delays, V2G…) to ensure grid stability, and are commonly called prosumers \cite{Rathnayaka2012} \cite{Ramchurn}.

There seems to have a clear consensus on the benefit of having bidirectional communication flows between prosumers and the grid as most of the demand side management concepts have proposed such an architecture \cite{WuHamedHuangBook2011}. Nevertheless as the number of active prosumers is expected to rise, it is safe to assume there is a need for more complex communication patterns (such as coalitions) that will help to decrease the communication burden and in the mean time satisfy the multiple requirements of the power grid management. The formation of coalitions inside the smart grid environment could be applied to various types of agents such as self sufficient micro-grids \cite{Pahwa}, sizable and adjustable virtual power plants (VPP) \cite{Braun} \cite{Ramchurn}, or fleet of electric vehicles that back up the grid in some emergency situations (V2G) \cite{Ramchurn}. These are just a few use cases where the coalition of multiple agents can enhance the grid reliability and in the mean time reduce the communication burden.

In this paper, we focus on how to statistically improve the production stability by carefully forming coalitions of prosumers that have greater probability of staying in acceptable range of production. By using prediction techniques, we form coalitions that meet the contract values ranges proposed by the grid, enabling it to schedule its production accordingly. Meeting contract values for the prosumer are especially relevant in power trade conditions, where energy is traded based on day-ahead predictions. In this context, participants should try to minimize their prediction errors in order to maintain a stable state for the grid. They may even occur some penalties if the productions deviate from the initial contract values. However, it is pertinent for both side to maintain the production as stable as possible : for the prosumer, the stability (with renewable energy source) will impact its net gain, and for the power grid, it will helps to maintain its reliability.
